TensorAlloy: an automatic atomistic neural network program for alloys

### 2019-10-29 doc/papers/nn/manuscript.tex
Minor update.
The conclusion section is slightly modified.

\author[a]{Xin Chen}
\author[a]{Xing-Yu Gao}
\author[b]{Ya-Fan Zhao}
\author[b]{De-Ye Lin\corref{author}}
\author[a]{Wei-Dong Chu}
\author[a,b]{Hai-Feng Song\corref{author}}

\cortext[author] {Corresponding author.
\\\textit{E-mail address:} lindeye0716@163.com}
\address[a]{Institute of Applied Physics and Computational Mathematics, 
Beijing 100088, China}
\address[b]{CAEP Software Center for High Performance Numerical Simulation, 
Beijing 100088, China}

@@

In this work, we introduced our virtual atom approach and a smart way of 
constructing symmetry function based atomistic neural networks. 
With the virtual atom approach, the calculations of the symmetry function 
descriptors can be implemented within TensorFlow. Thus, we can now build direct 
computation graph from atomic positions to total energy, making the technical 
barrier of calculating NN-derived atomic forces and virial stress neglectable.
This new algorithm is implemented in our Python program, TensorAlloy.

>>>>

\author[a]{Xin Chen}
\author[a]{Xing-Yu Gao}
\author[b,a]{Ya-Fan Zhao}
\author[b,a]{De-Ye Lin\corref{author}}
\author[a]{Wei-Dong Chu}
\author[a,b]{Hai-Feng Song\corref{author}}

\cortext[author] {Corresponding author.
\textit{E-mail address:} lindeye0716@163.com, song\_haifeng@iapcm.ac.cn}
\address[a]{Institute of Applied Physics and Computational Mathematics, 
Beijing 100088, China}
\address[b]{CAEP Software Center for High Performance Numerical Simulation, 
Beijing 100088, China}

@@

In this work, we introduced our virtual atom approach and a smart way of 
constructing symmetry function based atomistic neural networks. 
With the virtual atom approach, the calculations of the symmetry function 
descriptors can be implemented within TensorFlow. Thus, we can now build direct 
computation graph from atomic positions to total energy, making the technical 
barrier of calculating NN-derived atomic forces and virial stress neglectable. 
Hence, not only energies and forces, but also virial stress, can be used to 
train atomistic neural networks. Our experiment also suggests that including 
virial stress in the total loss function can significantly improve the accuracy
of predicting stress. All the new algorithms are implemented in our open-source
Python program TensorAlloy.
